The problem and promise of scale in multilayer animal social networks

### 2020-02-11 paper/manuscript.Rmd
fin results reorg

<!-- TODO: discuss layer similarity for social threshold -->
In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased to
~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across all networks (Figure
\@ref(fig:socres)b). <!-- missing summer--> Connective redundancy increased
rapidly when groups were formed up to approximately 100 m threshold, followed by
a plateau and slight decrease at higher thresholds, presumably due to an
increase in summer forest degree at ~500 m (Figure \@ref(fig:socres)d). Taken
together, these results suggest the optimal social scale at which groups should
be assigned is likely somewhere between ~20-100 m based on the rate at which
network metrics stabilized. For ungulates, groups are often assigned based on 50
m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019),
suggesting that given similar quantities of data, ~50 m is likely an ideal
social scale for generating social networks in caribou and similar species.

<!-- landcover resolution
* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased
--> 
<!-- TODO: discuss things in a,b,c,d order consistently. They shouldn't be presented out of order -->
Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Connective redundancy decreased
with increasing landcover resolution due the decrease in connectivity of
individuals in winter forage habitats, resulting in a multilayer network where
neighbours were less frequently repeated in multiple layers <!-- TODO: I'm
having a hard time understanding this previous sentence -->
(Figure\@ref(fig:lcres)d). Layer similarity was generally stable for forest and
open habitats except for a contrasting increase in similarity for forest and
decrease in similarity for open habitats at 250 m landcover resolution (Figure
\@ref(fig:lcres)c). Layer similarity was not possible to calculate between
winter and summer forage because, at all landcover resolutions greater than 30 m
there were no individuals connected in the network layers. <!-- individuals
still used forage but in much lower proportion + lowered opportunity to
associate --> These results indicate the importance of matching landcover
resolution to scale of selection as well as ensuring the landcover product used
has a resolution fine enough to detect relevant landscape features and habitats.
<!-- TODO: how? This isn't clear enough for me to follow yet -->

<!-- nobs * common, though at different points - more observations until
stabilizing * we dont see the stabilizing/full plateau for connective redundancy
but appears to be coming.. * still some variability, especially for graph
strength because individuals are differently connected but broad strokes - they
stabilize with more observations -->
As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low numbers of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below approximately 75 observations for forest, approximately
210 observations for open and approximately 300 observations for forage (Figure
\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity
stabilized for all three landcover classes at approximately 200 observations for
forest and approximately 300 observations for open and forage landcover types.
Connective redundancy increased with increasing number of observations as
individuals became more connected to neighbours in multiple layers (Figure
\@ref(fig:nobs)d). Given the overall trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing the social dynamics across
contexts. <!-- TODO: I'm not sure this is relevant since this is the main way it
is already done, can we make this thought more relevant to picking scales or
multilayer networks in general? I think it's important for building robust
networks -->

<!-- win  length * increasing window length = increasingly similar layers and
increasingly redundant edges. more individuals have the opportunity to interact
* increasing window length also leads to increasing similarity between seasons
because seasons are less well defined/include more shoulder seasons * decreasing
graph strength at the upper end of window length in winter showing again
inclusion of more shoulder season * layers are more similarly relevant at high
window length -->
Contrasting winter and summer seasons became more similar with increasing window
length. Layer similarity between seasons increased consistently across landcover
class (Figure \@ref(fig:winlen)b). Individual graph strength and layer relevance
increased for all summer layers as individuals became more connected with
increasing window lengths (Figure \@ref(fig:winlen)a, Figure
\@ref(fig:winlen)b). These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.
<!-- TODO: ?? --> <!-- TODO: end with something highlighting this shows it's
important to properly define your season -->
<!-- Similarly, shifting window position of the summer season resulted in an
increase in number of connections between individuals. Layer relevance  -->
<!-- win position * increasing network connectivity in summer when the window
position is moved - these seasons are more similar than the original window
position * same theme shown in the connective redundancy * quite variable layer
similarity, not sure what to pull out of that one * increased graph strength for
winter down the middle, with generally increasing summer layers - again where
the season is including more shoulder season potentially -->
<!-- Shifting window position results showed increasing layer similarity  -->
**Missing: discussion of window position..**

>>>>

<!-- TODO: discuss layer similarity for social threshold -->
In general, individuals in multilayer networks became more connected as social
scale increased; however, this relationship varied by habitat type and season.
As social scale increased, graph strength for winter networks increased to
~100-200 m thresholds, followed by a plateau, while graph strength for summer
networks did not change as the social threshold increased (Figure
\@ref(fig:socres)a). Layer relevance increased for winter networks between 5 and
50 m social thresholds, then did not change for any habitat types which suggests
the winter habitat layers captured most, if not all, of the potential
connections an individual would have across these networks (Figure
\@ref(fig:socres)b). <!-- missing summer--> Connective redundancy increased
rapidly when groups were formed up to ~100 m threshold, followed by
a plateau and slight decrease at higher thresholds, presumably due to an
increase in summer forest degree at ~500 m (Figure \@ref(fig:socres)d). Taken
together, these results suggest the optimal social scale at which groups should
be assigned is likely somewhere between ~20-100 m based on the rate at which
network metrics stabilized. For ungulates, groups are often assigned based on 50
m threshold (Lingle 2003; Lesmeries et al. 2018; Peignier et al. 2019),
suggesting that given similar quantities of data, ~50 m is likely an ideal
social scale for generating social networks in caribou and similar species.

<!-- landcover resolution
* decreasing availability of patchy lichen = no edges in these layers, though some small proportion of relocations still exist in those layers
* decreasing connective redundancy because through resolution because lichen decreased in connectivity and landcovers became more homogeneous (?)
* decreasing winter lichen relevance because the degree + number of edges decreased
--> 
<!-- TODO: discuss things in a,b,c,d order consistently. They shouldn't be presented out of order -->
Increasing the scale of landcover resolution resulted in decreased proportion of
rare and patchy habitats, and low connectivity of individuals in these habitats.
In winter, layer relevance was stable for open and forest habitats but decreased
for forage habitats (Figure \@ref(fig:lcres)b). Layer similarity was generally
stable for forest and open habitats except for a contrasting increase in
similarity for forest and decrease in similarity for open habitats 250 m
landcover resolution (Figure \@ref(fig:lcres)c). Layer similarity was not
possible to calculate between winter and summer forage because, at all landcover
resolutions greater than 30 m there were no individuals connected in the network
layers. <!-- individuals still used forage but in much lower proportion +
lowered opportunity to associate --> Connective redundancy decreased with
increasing landcover resolution due the decrease in connectivity of individuals
in winter forage habitats, resulting in a multilayer network where neighbours
were less frequently repeated in multiple layers <!-- TODO: I'm having a hard
time understanding this previous sentence --> (Figure\@ref(fig:lcres)d).  These
results indicate the importance of matching landcover resolution to scale of
selection as well as ensuring the landcover product used has a resolution fine
enough to detect relevant landscape features and habitats. <!-- TODO: how? This
isn't clear enough for me to follow yet -->

<!-- nobs * common, though at different points - more observations until
stabilizing * we dont see the stabilizing/full plateau for connective redundancy
but appears to be coming.. * still some variability, especially for graph
strength because individuals are differently connected but broad strokes - they
stabilize with more observations -->

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics generally appeared to stabilize.
Like coarse landcover resolution (above), low numbers of observations were not
sufficient for capturing individuals in all contexts and layer similarity could
not be calculated below approximately 75 observations for forest, approximately
210 observations for open and approximately 300 observations for forage (Figure
\@ref(fig:nobs)c). Once sufficient observations were obtained, layer similarity
stabilized for all three landcover classes at approximately 200 observations for
forest and approximately 300 observations for open and forage landcover types.
Connective redundancy increased with increasing number of observations as
individuals became more connected to neighbours in multiple layers (Figure
\@ref(fig:nobs)d). Given the overall trend of these multilayer metrics
stabilizing after a certain number of observations are included, the results
suggest this sensitivity method could be useful for determining the number of
observations necessary for sufficiently describing the social dynamics across
contexts.

<!-- TODO: I'm not sure this is relevant since this is the main way it
is already done, can we make this thought more relevant to picking scales or
multilayer networks in general? I think it's important for building robust
networks -->

<!-- win  length * increasing window length = increasingly similar layers and
increasingly redundant edges. more individuals have the opportunity to interact
* increasing window length also leads to increasing similarity between seasons
because seasons are less well defined/include more shoulder seasons * decreasing
graph strength at the upper end of window length in winter showing again
inclusion of more shoulder season * layers are more similarly relevant at high
window length -->

Contrasting winter and summer seasons became more similar with increasing window
length. Individual graph strength and layer relevance increased for all summer
layers as individuals became more connected with increasing window lengths
(Figure \@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Layer similarity between
seasons increased consistently across landcover class (Figure
\@ref(fig:winlen)b).  These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation according to resource availability and presence of conspecifics.

<!-- TODO: end with something highlighting this shows it's
important to properly define your season -->

<!-- Similarly, shifting window position of the summer season resulted in an
increase in number of connections between individuals. Layer relevance  -->
<!-- win position * increasing network connectivity in summer when the window
position is moved - these seasons are more similar than the original window
position * same theme shown in the connective redundancy * quite variable layer
similarity, not sure what to pull out of that one * increased graph strength for
winter down the middle, with generally increasing summer layers - again where
the season is including more shoulder season potentially -->
<!-- Shifting window position results showed increasing layer similarity  -->
**Missing: discussion of window position..**
